Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-09 Response to reviewers.tex

\noindent (1) \emph{Generally speaking, predicting sales is regarded as a regression problem (numerical output) rather than classification (categorical one). Both CFS and RelieFF are originally designed for classification problem. When CFS is used for regression, please to introduce how to estimate correlations between each feature and output (total sales). Since RReliefF, as a variant of ReliefF, is special for regression, why do not the authors use RReliefF? }

\begin{verbatim}
In all our experiments we have applied  WEKA's implementation 
of the ReliefF algorithm in the regression problems. 
This version is called "Regressional ReliefF" or "RReliefF" for 
short, which was first introduced and implemented by Robnik-Sikonja 
and Kononenko (in ref. [73] for numeric targets). 
Therefore, we have clarified this point in the text to remove 
any ambiguity.
\end{verbatim}
% Antonio - TODO: say where is this clarification in the text (page/paragraph) 
\begin{verbatim}
For CSF, estimating the correlation between attributes is 
standard linear (Pearson's) correlation. The details have 
been added to the text to clarify this point.
\end{verbatim}
% Antonio - TODO: say where is this clarification in the text (page/paragraph)

~\\
\noindent (2) \emph{In sub-section 4.2, five methods are introduced, i.e.,M5P,kNN,RF,LR and SVM. In sub-section 5.1, why is MLP (multi-layer perceptron) with one hidden layer described ?}

\begin{verbatim}
The current paper includes in sub-section 
`2.1. Selecting an appropriate forecasting method' (former
sub-section 4.2) six methods: M5P, kNN, RF, LR, SVM, MLP,
 and ELM (requested by Reviewer #2). After having included
 ELM, new references have been added (the list of new references
 can be found at the end of this letter).

Moreover, as suggested by the Reviewer #2 (see his/her first comment), 
the results obtained with the two last methods have been included in 
this new version of the paper.
\end{verbatim}
% Antonio - TODO: say where are these results (table/figure/page)

@@

%------------------------------------------------------------------------------------
\section{Comments by Reviewer \#2}

\noindent \emph{This paper applies some machine learning technologies to address issues related to book sales. There are some revisions that should be addressed by authors: } \\

\noindent (1) \emph{The ANN and ELM (extreme learning machine) should be added into the experiments; }

\begin{verbatim}
Following the reviewer's request, we have conducted several new experiments 
and added the results of ANN (MLP) and ELM to Tables XX, YY, ZZ and
Figures AA, BB accordingly. 
Their results have been also analyzed with the rest of methods, in the 
paragraphs below each one of the new figures.
A description of both approaches have been also included in subsection 2.1.

In addition new references have been added to the paper, related to these 
methods, namely [REF_XX, REF_YY]. In any case, the list of new references
can be found at the end of this letter.
\end{verbatim}
% Antonio - TODO: Complete with the number of tables and figures, along with the new references

@@

~\\
\noindent (2) \emph{The authors should clarify their main contributions in the introduction parts.}

\begin{verbatim}
We have rewritten the introduction and included new paragraphs to better 
explain the problem and the aim of the paper. We have also remarked the
contribution with the paragraphs (see page XX):

@@

"Our intention in this paper is to find out the main factors influencing
sales in order to create a tool that the publisher can use to decide how
many books should be printed, as well as how to leverage these printed
copies to maximize sales using the decision variables under his control. 
That is why, using data obtained from a company that sells software for 
publishers, we analyse them and compute predictive models that can be 
mainly used as decision-aid tools for book publishers. With these models,
 publishers will be able to combine their expert knowledge about the market 
with the created forecasting models in order to get a reliable estimation of
 book sales, and, based on it, act consequently in order to maximize the 
books sold for a particular print run. This will improve the current 
decision flow that the publishers follow, which consist in analysing (in a
 subjective way) the quality of the book and its features (author, genre, 
etc), and take a `fuzzy' decision roughly between printing 300 copies 
(standard book) or 5000 (best seller).

Our main contribution is, thus, the development of the methodology to 
process book sales data in order to, first find out relevant variables, 
and then, use these variables to process the data to accurately estimate 
future sales. To our knowledge this is the first work in which regression 
methods have been applied to estimate sales for new launched books. 
Moreover, we have considered a real dataset of book sales (related to 
the Spanish market), which is another point to remark."

Also, in the following paragraphs, we have laid out our 
methodology to differentiate it from other approaches.
\end{verbatim}
% TODO: update with the correct page where those paragraphs can be found

@@

%------------------------------------------------------------------------------------
\section{Comments by Reviewer \#3}

\noindent \emph{There are several concerns should be considered.}\\

\noindent (1) \emph{In section introduction, this manuscript should describe the contribution of this work. }

\begin{verbatim}
The reviewer is right. The main contribution of this paper to the 
state of the art was not properly described. Thus, as stated above 
in the second response to Reviewer #2, we have clarified this in 
the introduction adding new sentences and the paragraph (see page XX):

### 2016-09-09 paper.tex
Erasing my last comments as @amorag addressed them

In general, forecasting the sales of cultural products can
only be based on the knowledge obtained from sales of other, similar, ones,
but the definition of ``similar'' itself is fuzzy and, sometimes,
subjective. Even if the author or the topic is known, making accurate
estimations of future sales of the new product is quite difficult, and
extremely important, so that production runs follow predicted sales.  
Indeed, several studies have demonstrated that improving sales
predictions, that is reducing the error in estimated sales, results in an enhancement in the whole production process \cite{Fildes2010,Saeed2008}, so not only the costs associated to the book itself are affected.
% (Paloma) I was about to change this second "associated" for "affected" (seems the right thing to do). However, what's after this comma is also confusing, given that we already said that is affects to the whole production process. Maybe who wrote this should re-think what he/she meant to say here and change it.
% Antonio - I guess it was a mistake. I think now it is correct.

Within the general area of cultural products, the problem of
predicting sales is specially acute for book publishers who, among other
providers of content in physical form, release new {\em products} more frequently than
other industries, so that they face the problem of predicting sales quite often. The issue, in this case, is to print an adequate number of copies but not too many, as the unsold volumes will lead to losses and sunk inventory cost, 
whereas if the number of printed copies was not enough, a new print
run can always be made, but this will result in temporary losses due to a lack of supply or in bad marketing for the customers, for instance. However, in practice predicting lower sales than the actual ones is not such a big problem because the new print run is ordered before the inventory is exhausted; 
% (Paloma) I think that the thing that should be highlighted here is that is not big deal because the print run is made _before_ the inventory is exhausted. I mean, the sentence highlights the fact that a new print run is made, and not that maybe the situation where there's any book never happens. 
% Suggestion:  However, in practice predicting lower sales than the actual ones is not such a big problem because the new print run is orderer before the inventory is exhausted;
% Antonio - fixed then
 nevertheless, this new print run presents the same problem as the
initial one of printing only as many as forecasted, although its cost
is not as high as the initial one. 
% (Paloma) Should we really say this next sentence? :\
%and we are not so concerned with
%this issue in this paper.
% Antonio - yes, no need to say this

>>>>

In general, forecasting the sales of cultural products can
only be based on the knowledge obtained from sales of other, similar, ones,
but the definition of ``similar'' itself is fuzzy and, sometimes,
subjective. Even if the author or the topic is known, making accurate
estimations of future sales of the new product is quite difficult, and
extremely important, so that production runs follow predicted sales.  
Indeed, several studies have demonstrated that improving sales
predictions, that is reducing the error in estimated sales, results in an enhancement in the whole production process \cite{Fildes2010,Saeed2008}, so not only the costs associated to the book itself are affected.

Within the general area of cultural products, the problem of
predicting sales is specially acute for book publishers who, among other
providers of content in physical form, release new {\em products} more frequently than
other industries, so that they face the problem of predicting sales quite often. The issue, in this case, is to print an adequate number of copies but not too many, as the unsold volumes will lead to losses and sunk inventory cost, 
whereas if the number of printed copies was not enough, a new print
run can always be made, but this will result in temporary losses due to a lack of supply or in bad marketing for the customers, for instance. However, in practice predicting lower sales than the actual ones is not such a big problem because the new print run is ordered before the inventory is exhausted; nevertheless, this new print run presents the same problem as the
initial one of printing only as many as forecasted, although its cost
is not as high as the initial one.
